FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-17 NewVersion/sections/Auxiliary.tex

\subsection{Finding the Most Specifc Overriding: \mostSpecificOverride}\label{sec:mostSpecificOverride}
The $\mostSpecific$ function only focuses on original method
implementations, all the hierarchical overriding methods are omitted
during that step. On the other hand, $\mostSpecificOverride(m, I, J)$
has the assumption that $J$ defines an original $m$, and this function
tries to find the interfaces with the most specific implementations that hierarchically overrides such an $m$. Formally,

@@

\begin{theorem}[Type Soundness]~\label{theorem_soundness}
If $\judgeewf \o {e : I}$ and $e \to^* e'$ with $e'$ a normal form, then $e'$ is 
a value $v$ with $\judgeewf \o {v:I}$.
\end{theorem}
\begin{proof}
Immediate from Theorem~\ref{theorem_subject} and Theroem~\ref{theorem_progress}.
\end{proof}
Note that in Theorem~\ref{theorem_progress}, ``$\#(\overline{x})$'' denotes the length of
$\overline{x}$.

>>>>

\subsection{Finding the Most Specific Overriding: \mostSpecificOverride}\label{sec:mostSpecificOverride}
The $\mostSpecific$ function only focuses on original method
implementations, all the hierarchical overriding methods are omitted
during that step. On the other hand, $\mostSpecificOverride(m, I, J)$
has the assumption that $J$ defines an original $m$, and this function
tries to find the interfaces with the most specific implementations that hierarchically overrides such an $m$. Formally,

@@

\begin{theorem}[Type Soundness]~\label{theorem_soundness}
If $\judgeewf \o {e : I}$ and $e \to^* e'$ with $e'$ a normal form, then $e'$ is 
a value $v$ with $\judgeewf \o {v:I}$.
\end{theorem}
\begin{proof}
Immediate from Theorem~\ref{theorem_subject} and Theorem~\ref{theorem_progress}.
\end{proof}
Note that in Theorem~\ref{theorem_progress}, ``$\#(\overline{x})$'' denotes the length of
$\overline{x}$.

### 2017-10-17 NewVersion/sections/Discussion.tex

\section{Discussion}\label{sec:discussion}
In this section, we will discuss the design space and reflect about some of the design decisions of our work. We relate 
our language to traits, Java interfaces as well as other languages. Furthermore we discuss
ways to improve our  work.\bruno{references please!!!} \haoyuan{Done}

@@

Nonetheless,
 C++ accepts the definition of $D$, but forbids later upcasts from $D$ to $A$ because of ambiguity. Our language is more conservative on definitions of interfaces compared to C++, but on the upside up-casts are not rejected. We could also loosen the model to accept definitions such as \lstinline|D|, and perform ambiguity check on upcasts and other expressions. However, we would need to handle more cases than C++. For instance, in the above program assume that $B.m$ and $C.m$ are hierarchical overrides on $A$. Then such a case is still a diamond.

>>>>

\section{Discussion}\label{sec:discussion}
In this section, we will discuss the design space and reflect about some of the design decisions of our work. We relate 
our language to traits, Java interfaces as well as other languages. Furthermore, we discuss
ways to improve our  work.\bruno{references please!!!} \haoyuan{Done}

@@

Nonetheless,
 C++ accepts the definition of $D$, but forbids later upcasts from $D$ to $A$ because of ambiguity. Our language is more conservative on definitions of interfaces compared to C++, but on the upside, up-casts are not rejected. We could also loosen the model to accept definitions such as \lstinline|D|, and perform ambiguity check on upcasts and other expressions. However, we would need to handle more cases than C++. For instance, in the above program assume that $B.m$ and $C.m$ are hierarchical overrides on $A$. Then such a case is still a diamond.

### 2017-10-17 NewVersion/sections/Overview.tex
small fixes
local

\subsection{Problem 2: Dynamic Dispatching}\label{subsec:problem2}
Using explicit upcasts for disambiguation helps when making calls to
classes with conflicting methods, but things
become more complicated with dynamic dispatching. Dynamic
dispatching is very common in OO programming in order for code reuse. Let us expand the previous
example a bit, by redefining those interfaces with more features:

@@

// main program
new DrawableSafeDeck().shuffleAndDraw() // SafeDeck.draw is called
\end{lstlisting}\vspace{3pt}
During the runtime, when \lstinline|this.draw()| in called,
the dynamic type of the receiver is \lstinline|DrawableSafeDeck|, but the static type is actually
\lstinline|Deck|. Here it is an instance of the \textit{hierarchical invocation}, which can be read as 
``finding the most specific \lstinline|draw| along the path \lstinline|Deck|''. The meaning of ``along path
\lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes until the
dynamic type. Finally \lstinline|SafeDeck.draw| is correctly returned.

>>>>

\subsection{Problem 2: Dynamic Dispatching}\label{subsec:problem2}
Using explicit upcasts for disambiguation helps when making calls to
classes with conflicting methods, but things
become more complicated with dynamic dispatching. Dynamic
dispatching is very common in OO programming for code reuse. Let us expand the previous
example a bit, by redefining those interfaces with more features:

@@

// main program
new DrawableSafeDeck().shuffleAndDraw() // SafeDeck.draw is called
\end{lstlisting}\vspace{3pt}
During the runtime, when \lstinline|this.draw()| in called,
the dynamic type of the receiver is \lstinline|DrawableSafeDeck|, but the static type is actually
\lstinline|Deck|. Here it is an instance of the \textit{hierarchical invocation}, which can be read as 
``finding the most specific \lstinline|draw| along the path \lstinline|Deck|''. The meaning of ``along path
\lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes up to the
dynamic type \lstinline|DrawableSafeDeck|. Finally \lstinline|SafeDeck.draw| is correctly returned.
